{\LARGE Basis Choice for Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}

### 2022-02-09 Paper/main.tex
Grammarly Run

	\paragraph{Monomial Basis}\label{Monomial_basis}
	A straightforward idea to approximate functions in $\mathbb{L}^2[0,1]$ is to take inspiration from the well known Taylor expansion and to use monomials of increasing degree as a basis. For entire functions $f(t)$, e.g. polynomials, the exponential function or trigonometric functions, we can express the function as a potentially infinite, but converging sum of weighted monomials.
	\begin{equation}\label{Taylor_expansion}
		f(t) = \sum_{i = 1}^{\infty}a_i t^i \quad \text{where} \quad a_i = \frac{f^{(i)}(0)}{i!}
	\end{equation}

	The monomials are only a basis for the space of entire functions and not for $\mathbb{L}^2[0,1]$. But even for functions that do not fall into this category, like the logarithm, using a truncated Taylor expansion around a chosen point can lead to reasonable approximations around this specific point or even on $\mathbb{R}$ as a whole. From this idea, it is natural to use the monomials as a potential basis for approximation. \\
	As in the case of the Taylor expansion, it is not necessary to approximate a function around zero as shown above, instead one can introduce a shift parameter. This shift parameter $\alpha$ is often chosen such that the monomials are evaluated at the center point of the domain of the function.
	\begin{equation}
		\phi_{i}^{M}(t) = (t-\alpha)^i, \quad i \in \mathcal{I}
	\end{equation}

	Due to the implementation of our simulation, we will limit our paper to the case of $\alpha = 0$. However, a different choice of $\alpha$ could lead to improvements in performance of the Monomial basis.
	As the monomials are not pairwise orthogonal, this basis is prone to collinearity problems, which can result in numerically unstable estimates. This restricts the number of basis functions that can be used in the estimation procedures limiting its ability to capture pronounced local peculiarities. These problems will be addressed in more detail in later parts of this paper. The limitation to a low number of monomials can additionally lead to undesirable behavior away from the point of evaluation (cf. \cite{ramsay_functional_2005}).
	\vspace{-0.2cm}

@@

	Typically, the series is represented in the so called amplitude-phase form. This, however, is impractical for the estimation procedures shown in the later parts of this paper due to the phase shift parameter. Therefore, rewriting the series in the sine-cosine form as shown above is necessary.	
	The Fourier basis for $\mathbb{L}^2[0,1]$ is thus given by the following sequence of functions defined on $[0,1]$ directly corresponding to the terms of the sine-cosine form of the Fourier series.

	\begin{equation}
		\phi_{i}^{F}(x) = 
		\begin{cases}
			1 & \text{if} \quad i = 1\\
			\sqrt{2} \cos(\pi i x) & \text{if} \quad i \quad \text{is even} \\
			\sqrt{2} \sin(\pi (i-1)x) & \text{otherwise}
		\end{cases}
	\end{equation}
	To stay true to the original amplitude-phase form it is reasonable to restrict the number of Fourier basis functions to odd numbered values. The Fourier basis' elements exhibit a cyclical behavior which is useful to expand functions that represent a periodic or seasonal underlying process. The Fourier basis is especially suitable to expand functions with a similar curvature across the domain, generally resulting in uniformly smooth expansions. (cf. \cite{ramsay_functional_2005})
	\vspace{-0.2cm}

	\paragraph{B-spline Basis} Following chapter 3.5 from \cite{ramsay_functional_2005}, splines are defined by first dividing an interval of interest $[\tau_0, \tau_L]$ into $L$ subintervals of non-negative length divided by a non-decreasing sequence of points $(\tau_l)_{l = 1,\dots, L-1}$ called knots. On each subinterval, a spline is a polynomial of order $m = n+1$ where $n$ is its degree. If there are no multiplicities in the set of knots, the polynomials on neighboring subintervals share derivatives up to order $m-2$ at the boundary knot $\tau_l$. A typical case that is often used in practice is an equidistant grid of knots. In some settings, however, it can be sensible to place multiple knots at the same value to replicate specific properties of the data structure allowing for a reduced number of matching derivatives at the corresponding knots. For the purposes of this paper, we will focus on the case of equidistant knots without multiplicity at inner knots.\\

@@

	As this equation references knots that are not defined by the original vector of knots, implementations of this algorithm typically repeat the knots at the boundaries of the interval, $\tau_0$ and $\tau_L$ an additional $m$ times. This padding of the knot vector then allows to calculate every object that is needed for the definition of the basis over the original set of knots.\\	
	This, however, does not lead to a basis of $\mathbb{L}^2[0,1]$ as the closed span of this finite sequence of functions is not equal to $\mathbb{L}^2[0,1]$. To focus on specific approximation errors in the later parts of this paper, we will, however, assume that a B-spline basis representation of a function in $\mathbb{L}^2[0,1]$ will serve as a sufficient approximation for an appropriately chosen number of B-spline basis functions. 
	As the B-spline basis does not have infinitely many elements as the full Monomial or Fourier bases do, it is slightly misleading to speak of truncating the B-spline basis at a truncation parameter $L$ in later parts of this paper. For the sake of keeping the notation reasonably concise, we will still keep this notation. However, by convention, truncating a B-spline basis at truncation parameter $L$ shall mean using a B-spline basis consisting of $L$ functions from this point on.

	\subsection{Approximation and Smoothing via Basis Truncation}
	Realized curves from a data set can be expressed in terms of a chosen functional basis. For this expansion, it is  possible to use a complete basis of $\mathbb{L}^2[0,1]$. In many cases this is not a desirable approach as this expansion can introduce high amounts of variance or even lead to the approximation of noise in the sample curves, the latter being a typical case of overfitting. To combat this problem, smoothing methods such as, for example, acceleration penalties are employed to enforce a degree of smoothness in the analyzed curves. On the other hand, important information on the curves could be missed by smoothing the data too much by giving too much weight to a chosen penalty term leading to oversmoothing and loss of valuable information. This is a typical occurence of the Bias-Variance tradeoff.\\

	A different approach that is atypical in practice, is to enforce smoothing by limiting the number of basis functions in the approximation of the functional objects. Here, the parameter of choice is not a weighting term for the penalty, but the number of basis functions. Exploring this alternative smoothing method in two different estimation procedures is the main focus of this paper. A truncated basis expansion as described above is given in Equation \ref{basis_exp}.
	\begin{equation}\label{basis_exp}
		X(\omega_0) = x(t) = \sum_{j \in \mathcal{I}} A_j(\omega_0) \phi_j(t) = \sum_{j = 1}^{L} A_j(\omega_0) \phi_j(t) + \delta(t) \approx \sum_{j = 1}^{L} A_j(\omega_0) \phi_j(t)
	\end{equation}

	where $\delta(t)$ is the truncation error and $L \leq \max\limits_{j \in \mathcal{I}}(j)$ for all $L \in \mathcal{I}$.  In later parts, this approximation error is explicitly denoted in the derivation and then omitted for the final approximations. $L$ can be chosen subjectively, but also through applying data-driven methods such as Cross-Validation. Figure \ref{Different_Expansions} shows the effect of choosing different numbers of basis functions for one observation of the Near-Infrared Spectroscopy data set which is used in the later parts of this paper and exemplifies the tradeoffs that are at the core of the truncation parameter choice.

@@

	Then, the operator $K$ has orthonormal basis functions $\nu^{m} \in \mathbb{L}^{2}[0,1]$ each corresponding to an Eigenvalue $\lambda^{m}$ since it is a positive compact self-adjoint operator (cf. \cite{alexanderian_KLexpansion_2015}).
	Theoretical considerations lead to the result that $X$ can be represented in the following form, called its Karhunen-Lo\'{e}ve expansion.\footnote{Proofs for these theorems are provided in Appendix \ref{Proof1} and \ref{Proof2}.} 
	\begin{equation}\label{KarhunenLoeve}
		X(\omega)(t) = \mu(t) + \sum_{m = 1}^{\infty} \xi^m(\omega) \nu^m(t), \quad \xi^m(\omega) =  \int_{0}^{1} \left(X(\omega)(s) - \mu(s)\right) \nu^m(s) \mathrm{d}s
	\end{equation}

@@

	As in the well known setting of principal component analysis, the Eigenvalues correspond to the variance in the random function that is explained by the corresponding Eigenfunction. 
	Therefore, ordering the the Eigenfunctions according to their their corresponding Eigenvalues $\lambda^{1} \geq \lambda^{2} \geq \dots \geq 0$ is useful for approximation purposes. Due to this property a functional observation can often be approximated well by using a limited number of the Eigenfunctions of its generating random process. Moreover, our data generating process for the simulation study is based on this property as explained in Section \ref{similar_curves}.\\
	In the scalar setting, a similar consideration leads to the concept of principal components, which can be extended to the functional setting. Let $\{x_1(t), \dots, x_n(t)\}$ be a set of i.i.d. realizations generated by a random function $X(\omega) \mapsto \mathbb{L}^2[0,1]$.
	Define the following sample analogs for the mean and covariance functions.
	\begin{equation}
		\hat{\mu}(t) = \frac{1}{N}\sum_{i = 1}^{N}x_i(t)
	\end{equation}
	\begin{equation}
		\hat{c}(t,s) = \frac{1}{N} \sum_{i = 1}^{N} \left(x_i(t) - \hat{\mu}(t)\right) \left(x_i(s) - \hat{\mu}(s)\right)
	\end{equation}

@@

	In the following, we will call the $\hat{\nu}^m(s)$ functional principal components to distinguish the sample analogs from the theoretical Eigenfunctions $\nu^m(s)$. As in the case of ordinary principal components, the number of functional principal components corresponding to non-zero Eigenvalues is limited (cf. chapter 8.2.3 \cite{ramsay_functional_2005}). As each curve is infinite dimensional, there is no upper limit to this number due to the dimensionality. However, the number of curves still imposes an upper limit of $N-1$ non-zero Eigenvalues, where $N$ is the number of curves in the data set.
	These sample analogs naturally lead to the following representation of each sample curve $x_i(t)$.
	\begin{equation}
		x_i(t) = \hat{\mu}(t) + \sum_{j = 1}^{N-1} \hat{\xi}_{i}^{m} \hat{\nu}^{m}(t)
	\end{equation}
	where the $\hat{\xi}_{i}^m$ are derived as 
	\begin{equation}
		\hat{\xi}_i^m(\omega) = \langle x_i - \hat{\mu}, \hat{\nu}^m\rangle = \int_{0}^{1} \left(x_i(s) - \hat{\mu}(s)\right) \hat{\nu}^m(s) \mathrm{d}s
	\end{equation}
	In reality, these calculations are often implemented using basis representations of both the functional principal components $\hat{\nu}^m$ and the observations $x_i(t)$ leading to the following representation. For the sake of clarity, the following equation assumes that the bases used for the expansion of both the observations and the coefficient function are true bases of $\mathbb{L}^2[0,1]$ and can therefore be used to express the corresponding objects exactly.
	\begin{equation}\label{FPCA_basis_expansion}
		\begin{split}
			\hat{\xi}_{i}^m & = \int_{0}^{1} {\color{red}\left( x_i(s) - \hat{\mu}(s)\right)} {\color{blue}\hat{\nu}^m(s)} \mathrm{d}s
			= \int_{0}^{1} {\color{red}\left(\sum_{j \in \mathcal{I}} a_{i,j} \phi_j(s)\right)} {\color{blue}\left(\sum_{k \in \mathcal{L}} d_{k}^m \psi_{k}(s)\right)} \mathrm{d}s \\
			& = \int_{0}^{1} {\color{red}\left(\sum_{j = 1}^{J} a_{i,j} \phi_j(s) + \delta_i^J(s)\right)} {\color{blue}\left(\sum_{k = 1}^{K} d_{k}^m \psi_{k}(s) + \delta_{\nu}^{m,K}(s)\right)} \mathrm{d}s \\
			& = \sum_{j = 1}^{J} \left[a_{i,j}\sum_{k = 1}^{K} d_{k}^m \int_{0}^{1} \phi_j(s) \psi_{k}(s)\mathrm{d}s \right] +  \sum_{k = 1}^{K} d_{k}^m \int_{0}^{1} \delta_i^J(s) \psi_{k}(s) \mathrm{d}s \\
			& \quad + \sum_{j = 1}^{J} a_{i,j} \int_{0}^{1}\phi_j(s) \delta_{\nu}^{m,K}(s) \mathrm{d}s + \int_{0}^{1} \delta_i^J(s) \delta_{\nu}^{m,K}(s) \mathrm{d}s
		\end{split}
	\end{equation}
	In practice, a typical choice is to use the same basis $\left(\phi_j(t)\right)_{j \in \mathcal{I}}$ and the same truncation parameter $L$ for the basis expansion of the demeaned observations $\left(x_i(t) - \hat{\mu}(t)\right)$ and the functional principal components $\hat{\nu}^m$. This leads to the following simplification of Equation \ref{FPCA_basis_expansion}.
	\begin{equation}\label{score_approx}
		\begin{split}
			\hat{\xi}_{i}^m &= \sum_{j = 1}^{L} \left[a_{i,j}\sum_{k = 1}^{L} d_{k}^m \int_{0}^{1} \phi_j(s) \phi_{k}(s)\mathrm{d}s \right] +  \sum_{k = 1}^{L} d_{k}^m \int_{0}^{1} \delta_i^L(s) \phi_{k}(s) \mathrm{d}s \\
			& \quad + \sum_{j = 1}^{L} a_{i,j} \int_{0}^{1}\phi_j(s) \delta_{\beta}^L(s) \mathrm{d}s + \int_{0}^{1} \delta_i^L(s) \delta_{\beta}^L(s) \mathrm{d}s
		\end{split}
	\end{equation}
	And we can define the following objects:
		\begin{align}
			\tilde{\xi}^{m,L}_{i} & := \sum_{j = 1}^{L} \left[a_{i,j}\sum_{k = 1}^{L} b_{k}^m \int_{0}^{1} \phi_j(s) \phi_{k}(s)\mathrm{d}s \right] 
			& \delta_{\xi, i}^L & := \hat{\xi}_{i}^m - \tilde{\xi}^{m,L}_{i} \\
			\tilde{\nu}^{m,L}(t) & := \sum_{k = 1}^{L} d_{k}^m \phi_{k}(t) 
			& \delta_{\nu}^{m, L}(t) & := \hat{\nu}^m(t) - \tilde{\nu}^{m,L}(t)
		\end{align}

	This method of deriving or approximating the Eigenfunctions and scores from a data set is introduced in \cite{ramsay_functional_2005} (chapter 8.4.2) and implemented in the R-package fda. The following considerations and results of the simulation study might therefore serve as information about the performance of this method in a scenario where a limited number of basis functions is provided to the method instead of using more conventional smoothing approaches.

	\subsection{Scalar-on-Function Regression}\label{Scalar_on_function_regression}
	In the simple scalar setting, one of the most important tools in econometrics is linear regression. Its goal is twofold: to gain information about the dependency between variables, but also to allow for prediction. To motivate the jump from multivariate regression to scalar-on-function regression, assume a data generating process as follows.
	\begin{equation}
		Y = X\beta + \epsilon
	\end{equation}

	Here, $Y$ is the vector of response variables, $X$ is the matrix containing the corresponding regressors in its columns and $\beta = (\beta_0, \beta_1, \: \dots, \beta_p)'$ is the vector containing the unknown coefficients.
	In this finite dimensional setting one important question is how to estimate the unknown coefficients $\beta$. The most well known estimator in all of econometrics, the Ordinary Least Squares (OLS) estimator, fulfills this purpose under a set of assumptions.
	\begin{equation}
		\hat{\beta}_{OLS} = (X'X)^{-1}X'Y
	\end{equation}

	The concept of linear regression can be extended to a setting of functional data, where a scalar response variable is assumed to be dependent on a functional regressor. 
	Even though integrating over the product of an observation with the coefficient function is not the only functional that can be used to create a data generating process involving functional observations, it is the most typical as it naturally extends the intuition from multiple linear regression to the realm of infinite-dimensional objects. Therefore, we will always assume a data generating process as follows in this paper.
	\begin{equation}\label{DGP}
		Y(\omega) = \alpha + \int_{0}^{1} \beta(s)X(\omega)(s) \mathrm{d}s + \epsilon(\omega)
	\end{equation}

@@

	\subsubsection{Estimation using Basis-Representation}\label{basis_exp_transf}
	The most common way to make this problem tractable is via a basis representation of $\beta(t)$. Therefore, let $\{\phi_i(t) \: \vert \: i \in \mathcal{I}\}$ be a basis of $\mathbb{L}^2[0,1]$ and represent $\beta(t)$ in terms of this basis.
	\begin{equation}
		\beta(t) = \sum_{j \in \mathcal{I}} b_j \phi_j(t)
	\end{equation}
	This enables us to write equation \ref{DGP} using this representation to obtain a formulation as a sum of scalar random variables $Z_j(\omega)$.

	\begin{equation}
		\begin{split}
			Y(\omega) & = \alpha + \int_{0}^{1} {\color{blue}\beta(s)} X(\omega)(s)\mathrm{d}s + \epsilon(\omega)
			= \alpha + \int_{0}^{1}\left[{\color{blue}\left(\sum_{j \in \mathcal{I}} b_j \phi_j(s)\right)} X(\omega)(s) \right]\mathrm{d}s + \epsilon(\omega) \\
			& = \alpha + \sum_{j \in \mathcal{I}} \left[b_j \textcolor{red}{\int_{0}^{1} X(\omega)(s) \phi_j(s)\mathrm{d}s}\right] + \epsilon(\omega)
		      = \alpha + \sum_{j \in \mathcal{I}} b_j \textcolor{red}{Z_j(\omega)} + \epsilon(\omega)
		\end{split}
	\end{equation}

@@

	Then an OLS estimator can be calculated in the usual way to obtain an estimate for the values of $\alpha$ and $b_j$ and an estimate of the coefficient function can be derived accordingly.
	\begin{equation}
		b^L = \left(Z'Z\right)^{-1}Z'Y \in \mathbb{R}^{L+1} \quad \hat{\alpha} = b_{1}^{L} \quad \hat{\beta}^L(t) = \sum_{j = 1}^{J} b_{j+1}^L \phi_j(t)
	\end{equation}

@@

	\subsection{Motivation}
	\label{sim_motivation}

>>>>

	\paragraph{Monomial Basis}\label{Monomial_basis}
	A straightforward idea to approximate functions in $\mathbb{L}^2[0,1]$ is to take inspiration from the well-known Taylor expansion and to use monomials of increasing degree as a basis. For entire functions $f(t)$, such as polynomials, the exponential function, or trigonometric functions, we can express the function as a potentially infinite but converging sum of weighted monomials.
	\begin{equation}\label{Taylor_expansion}
		f(t) = \sum_{i = 1}^{\infty}a_i t^i \quad \text{where} \quad a_i = \frac{f^{(i)}(0)}{i!}
	\end{equation}

	The monomials are only a basis for the space of entire functions and not for $\mathbb{L}^2[0,1]$. Nevertheless, even for functions that do not fall into this category, using a truncated Taylor expansion around a chosen point can lead to reasonable approximations around this specific point or even on $\mathbb{R}$ as a whole. From this idea, it is natural to use the monomials as a potential basis for approximation. \\
	As in the case of the Taylor expansion, it is not necessary to approximate a function around zero, as shown above. Instead, one can introduce a shift parameter. This shift parameter $\alpha$ is often chosen such that the monomials are evaluated at the center point of the domain of the function.
	\begin{equation}
		\phi_{i}^{M}(t) = (t-\alpha)^i, \quad i \in \mathcal{I}
	\end{equation}

	Due to the implementation of our simulation, we will limit our paper to the case of $\alpha = 0$. However, a different choice of $\alpha$ could lead to improvements in the performance of the Monomial basis.
	As the monomials are not pairwise orthogonal, this basis is prone to collinearity problems, which can result in numerically unstable estimates. This restricts the number of basis functions that can be used in the estimation procedures limiting its ability to capture pronounced local peculiarities. These problems will be addressed in more detail in later parts of this paper. The limitation to a low number of monomials can additionally lead to undesirable behavior away from the point of evaluation (cf. \cite{ramsay_functional_2005}).
	\vspace{-0.2cm}

@@

	Typically, the series is represented in the so-called amplitude-phase form. This, however, is impractical for the estimation procedures shown in the later parts of this paper due to the phase shift parameter. Therefore, rewriting the series in the sine-cosine form, as shown above, is necessary.
	The Fourier basis for $\mathbb{L}^2[0,1]$ is thus given by the following sequence of functions defined on $[0,1]$ directly corresponding to the terms of the sine-cosine form of the Fourier series.

	\begin{equation}
		\phi_{i}^{F}(x) = 
		\begin{cases}
			1 & \text{if} \quad i = 1\\
			\sqrt{2} \cos(\pi i x) & \text{if} \quad i \quad \text{is even} \\
			\sqrt{2} \sin(\pi (i-1)x) & \text{otherwise}
		\end{cases}
	\end{equation}
	To stay true to the original amplitude-phase form, it is reasonable to restrict the number of Fourier basis functions to odd-numbered values. The Fourier basis' elements exhibit a cyclical behavior which is useful to expand functions that represent a periodic or seasonal underlying process. The Fourier basis is especially suitable to expand functions with a similar curvature across the domain, generally resulting in uniformly smooth expansions. (cf. \cite{ramsay_functional_2005})
	\vspace{-0.2cm}

	\paragraph{B-spline Basis} Following chapter 3.5 from \cite{ramsay_functional_2005}, splines are defined by first dividing an interval of interest $[\tau_0, \tau_L]$ into $L$ subintervals of non-negative length divided by a non-decreasing sequence of points $(\tau_l)_{l = 1,\dots, L-1}$ called knots. On each subinterval, a spline is a polynomial of order $m = n+1$ where $n$ is its degree. If there are no multiplicities in the set of knots, the polynomials on neighboring subintervals share derivatives up to order $m-2$ at the boundary knot $\tau_l$. A typical case that is often used in practice is an equidistant grid of knots. In some settings, however, it can be sensible to place multiple knots at the same value to replicate specific properties of the data structure, allowing for a reduced number of matching derivatives at the corresponding knots. For the purposes of this paper, we will focus on the case of equidistant knots without multiplicity at inner knots.\\

@@

	As this equation references knots that are not defined by the original vector of knots, implementations of this algorithm typically repeat the knots at the boundaries of the interval, $\tau_0$ and $\tau_L$, an additional $m$ times. This padding of the knot vector then allows calculating every object that is needed for the definition of the basis over the original set of knots.\\	
	This, however, does not lead to a basis of $\mathbb{L}^2[0,1]$ as the closed span of this finite sequence of functions is not equal to $\mathbb{L}^2[0,1]$. To focus on specific approximation errors in the later parts of this paper, we will, however, assume that a B-spline basis representation of a function in $\mathbb{L}^2[0,1]$ will serve as a sufficient approximation for an appropriately chosen number of B-spline basis functions. 
	As the B-spline basis does not have infinitely many elements as the full Monomial or Fourier bases do, it is slightly misleading to speak of truncating the B-spline basis at a truncation parameter $L$ in later parts of this paper. For the sake of keeping the notation reasonably concise, we will still keep this notation. However, by convention, truncating a B-spline basis at truncation parameter $L$ shall mean using a B-spline basis consisting of $L$ functions from this point on.

	\subsection{Approximation and Smoothing via Basis Truncation}
	Realized curves from a data set can be expressed in terms of a chosen functional basis. For this expansion, it is possible to use a complete basis of $\mathbb{L}^2[0,1]$. In many cases, this is not a desirable approach as this expansion can introduce high amounts of variance or even lead to the approximation of noise in the sample curves, the latter being a typical case of overfitting. To combat this problem, smoothing methods such as, for example, acceleration penalties are employed to enforce a degree of smoothness in the analyzed curves. On the other hand, important information on the curves could be missed by smoothing the data too much by giving too much weight to a chosen penalty term leading to oversmoothing and loss of valuable information. This is a typical occurrence of the Bias-Variance tradeoff.\\

	A different approach that is atypical in practice is to enforce smoothing by limiting the number of basis functions in the approximation of the functional objects. Here, the parameter of choice is not a weighting term for the penalty but the number of basis functions. Exploring this alternative smoothing method in two different estimation procedures is the main focus of this paper. A truncated basis expansion as described above is given in Equation \ref{basis_exp}.
	\begin{equation}\label{basis_exp}
		X(\omega_0) = x(t) = \sum_{j \in \mathcal{I}} A_j(\omega_0) \phi_j(t) = \sum_{j = 1}^{L} A_j(\omega_0) \phi_j(t) + \delta(t) \approx \sum_{j = 1}^{L} A_j(\omega_0) \phi_j(t)
	\end{equation}

	where $\delta(t)$ is the truncation error and $L \leq \max\limits_{j \in \mathcal{I}}(j)$ for all $L \in \mathcal{I}$.  In later parts, this approximation error is explicitly denoted in the derivation and then omitted for the final approximations. $L$ can be chosen subjectively, but also through applying data-driven methods such as Cross-Validation. Figure \ref{Different_Expansions} shows the effect of choosing different numbers of basis functions for one observation of the Near-Infrared Spectroscopy data set, which is used in the later parts of this paper and exemplifies the tradeoffs at the core of the truncation parameter choice.

@@

	Then, the operator $K$ has orthonormal basis functions $\nu^{m} \in \mathbb{L}^{2}[0,1]$, each corresponding to an Eigenvalue $\lambda^{m}$ since it is a positive compact self-adjoint operator (cf. \cite{alexanderian_KLexpansion_2015}).
	Theoretical considerations lead to the result that $X$ can be represented in the following form, called its Karhunen-Lo\'{e}ve expansion.\footnote{Proofs for these theorems are provided in Appendix \ref{Proof1} and \ref{Proof2}.} 
	\begin{equation}\label{KarhunenLoeve}
		X(\omega)(t) = \mu(t) + \sum_{m = 1}^{\infty} \xi^m(\omega) \nu^m(t), \quad \xi^m(\omega) =  \int_{0}^{1} \left(X(\omega)(s) - \mu(s)\right) \nu^m(s) \mathrm{d}s
	\end{equation}

@@

	As in the well-known setting of principal component analysis, the Eigenvalues correspond to the variance in the random function explained by the corresponding Eigenfunction. 
	Therefore, ordering the Eigenfunctions according to their corresponding Eigenvalues $\lambda^{1} \geq \lambda^{2} \geq \dots \geq 0$ is useful for approximation purposes. Due to this property, a functional observation can often be approximated well by using a limited number of the Eigenfunctions of its generating random process. Moreover, our data generating process for the simulation study is based on this property as explained in Section \ref{similar_curves}.\\
	In the scalar setting, a similar consideration leads to the concept of principal components, which can be extended to the functional setting. Let $\{x_1(t), \dots, x_n(t)\}$ be a set of i.i.d. realizations generated by a random function $X(\omega) \mapsto \mathbb{L}^2[0,1]$.
	Define the following sample analogs for the mean and covariance functions.
	\begin{equation}
		\hat{\mu}(t) = \frac{1}{N}\sum_{i = 1}^{N}x_i(t)
	\end{equation}
	\begin{equation}
		\hat{c}(t,s) = \frac{1}{N} \sum_{i = 1}^{N} \left(x_i(t) - \hat{\mu}(t)\right) \left(x_i(s) - \hat{\mu}(s)\right)
	\end{equation}

@@

	In the following, we will call the $\hat{\nu}^m(s)$ functional principal components to distinguish the sample analogs from the theoretical Eigenfunctions $\nu^m(s)$. As in the case of ordinary principal components, the number of functional principal components corresponding to non-zero Eigenvalues is limited (cf. chapter 8.2.3 \cite{ramsay_functional_2005}). As each curve is infinite-dimensional, there is no upper limit to this number due to the dimensionality. However, the number of curves still imposes an upper limit of $N-1$ non-zero Eigenvalues, where $N$ is the number of curves in the data set.
	These sample analogs naturally lead to the following representation of each sample curve $x_i(t)$.
	\begin{equation}
		x_i(t) = \hat{\mu}(t) + \sum_{j = 1}^{N-1} \hat{\xi}_{i}^{m} \hat{\nu}^{m}(t)
	\end{equation}
	where the $\hat{\xi}_{i}^m$ are derived as 
	\begin{equation}
		\hat{\xi}_i^m(\omega) = \langle x_i - \hat{\mu}, \hat{\nu}^m\rangle = \int_{0}^{1} \left(x_i(s) - \hat{\mu}(s)\right) \hat{\nu}^m(s) \mathrm{d}s
	\end{equation}
	In reality, these calculations are often implemented using basis representations of both the functional principal components $\hat{\nu}^m$ and the observations $x_i(t)$ leading to the following representation. For the sake of clarity, the following equation assumes that the bases used for the expansion of both the observations and the coefficient function are proper bases of $\mathbb{L}^2[0,1]$ and can therefore be used to express the corresponding objects exactly.
	\begin{equation}\label{FPCA_basis_expansion}
		\begin{split}
			\hat{\xi}_{i}^m & = \int_{0}^{1} {\color{red}\left( x_i(s) - \hat{\mu}(s)\right)} {\color{blue}\hat{\nu}^m(s)} \mathrm{d}s
			= \int_{0}^{1} {\color{red}\left(\sum_{j \in \mathcal{I}} a_{i,j} \phi_j(s)\right)} {\color{blue}\left(\sum_{k \in \mathcal{L}} d_{k}^m \psi_{k}(s)\right)} \mathrm{d}s \\
			& = \int_{0}^{1} {\color{red}\left(\sum_{j = 1}^{J} a_{i,j} \phi_j(s) + \delta_i^J(s)\right)} {\color{blue}\left(\sum_{k = 1}^{K} d_{k}^m \psi_{k}(s) + \delta_{\nu}^{m,K}(s)\right)} \mathrm{d}s \\
			& = \sum_{j = 1}^{J} \left[a_{i,j}\sum_{k = 1}^{K} d_{k}^m \int_{0}^{1} \phi_j(s) \psi_{k}(s)\mathrm{d}s \right] +  \sum_{k = 1}^{K} d_{k}^m \int_{0}^{1} \delta_i^J(s) \psi_{k}(s) \mathrm{d}s \\
			& \quad + \sum_{j = 1}^{J} a_{i,j} \int_{0}^{1}\phi_j(s) \delta_{\nu}^{m,K}(s) \mathrm{d}s + \int_{0}^{1} \delta_i^J(s) \delta_{\nu}^{m,K}(s) \mathrm{d}s
		\end{split}
	\end{equation}
	In practice, a typical choice is to use the same basis $\left(\phi_j(t)\right)_{j \in \mathcal{I}}$ and the same truncation parameter $L$ for the basis expansion of the demeaned observations $\left(x_i(t) - \hat{\mu}(t)\right)$ and the functional principal components $\hat{\nu}^m$. This leads to the following simplification of Equation \ref{FPCA_basis_expansion}.
	\begin{equation}\label{score_approx}
		\begin{split}
			\hat{\xi}_{i}^m &= \sum_{j = 1}^{L} \left[a_{i,j}\sum_{k = 1}^{L} d_{k}^m \int_{0}^{1} \phi_j(s) \phi_{k}(s)\mathrm{d}s \right] +  \sum_{k = 1}^{L} d_{k}^m \int_{0}^{1} \delta_i^L(s) \phi_{k}(s) \mathrm{d}s \\
			& \quad + \sum_{j = 1}^{L} a_{i,j} \int_{0}^{1}\phi_j(s) \delta_{\beta}^L(s) \mathrm{d}s + \int_{0}^{1} \delta_i^L(s) \delta_{\beta}^L(s) \mathrm{d}s
		\end{split}
	\end{equation}
	And we can define the following objects:
		\begin{align}
			\tilde{\xi}^{m,L}_{i} & := \sum_{j = 1}^{L} \left[a_{i,j}\sum_{k = 1}^{L} b_{k}^m \int_{0}^{1} \phi_j(s) \phi_{k}(s)\mathrm{d}s \right] 
			& \delta_{\xi, i}^L & := \hat{\xi}_{i}^m - \tilde{\xi}^{m,L}_{i} \\
			\tilde{\nu}^{m,L}(t) & := \sum_{k = 1}^{L} d_{k}^m \phi_{k}(t) 
			& \delta_{\nu}^{m, L}(t) & := \hat{\nu}^m(t) - \tilde{\nu}^{m,L}(t)
		\end{align}

	This method of deriving or approximating the Eigenfunctions and scores from a data set is introduced in \cite{ramsay_functional_2005} (chapter 8.4.2) and implemented in the R-package fda. The following considerations and results of the simulation study might serve as information about the performance of this method in a scenario where a limited number of basis functions is provided to the method instead of using more conventional smoothing approaches.

	\subsection{Scalar-on-Function Regression}\label{Scalar_on_function_regression}
	In the simple scalar setting, one of the essential tools in econometrics is linear regression. Its goal is twofold: to gain information about the dependency between variables and allow for prediction. To motivate the jump from multivariate regression to scalar-on-function regression, assume a data generating process as follows.
	\begin{equation}
		Y = X\beta + \epsilon
	\end{equation}

	Here, $Y$ is the vector of response variables, $X$ is the matrix containing the corresponding regressors in its columns, and $\beta = (\beta_0, \beta_1, \: \dots, \beta_p)'$ is the vector containing the unknown coefficients.
	In this finite-dimensional setting, one important question is how to estimate the unknown coefficients $\beta$. The most famous estimator in all of econometrics, the Ordinary Least Squares (OLS) estimator, fulfills this purpose under a set of assumptions.
	\begin{equation}
		\hat{\beta}_{OLS} = (X'X)^{-1}X'Y
	\end{equation}

	The concept of linear regression can be extended to the setting of functional data, where a scalar response variable is assumed to be dependent on a functional regressor. 
	Even though integrating over the product of an observation with the coefficient function is not the only functional that can be used to create a data generating process involving functional observations, it is the most typical as it naturally extends the intuition from multiple linear regression to the realm of infinite-dimensional objects. Therefore, we will always assume a data generating process as follows in this paper.
	\begin{equation}\label{DGP}
		Y(\omega) = \alpha + \int_{0}^{1} \beta(s)X(\omega)(s) \mathrm{d}s + \epsilon(\omega)
	\end{equation}

@@

	\subsubsection{Estimation using Basis-Representation}\label{basis_exp_transf}
	The most common way to make this problem tractable is via a basis representation of $\beta(t)$. Therefore, let $\{\phi_i(t) \: \vert \: i \in \mathcal{I}\}$ be a basis of $\mathbb{L}^2[0,1]$ and represent $\beta(t)$ in terms of this basis.
	\begin{equation}
		\beta(t) = \sum_{j \in \mathcal{I}} b_j \phi_j(t)
	\end{equation}
	This enables us to write equation \ref{DGP} using this representation to obtain a formulation as a sum of scalar random variables $Z_j(\omega)$.	
	\begin{equation}
		\begin{split}
			Y(\omega) & = \alpha + \int_{0}^{1} {\color{blue}\beta(s)} X(\omega)(s)\mathrm{d}s + \epsilon(\omega)
			= \alpha + \int_{0}^{1}\left[{\color{blue}\left(\sum_{j \in \mathcal{I}} b_j \phi_j(s)\right)} X(\omega)(s) \right]\mathrm{d}s + \epsilon(\omega) \\
			& = \alpha + \sum_{j \in \mathcal{I}} \left[b_j \textcolor{red}{\int_{0}^{1} X(\omega)(s) \phi_j(s)\mathrm{d}s}\right] + \epsilon(\omega)
		      = \alpha + \sum_{j \in \mathcal{I}} b_j \textcolor{red}{Z_j(\omega)} + \epsilon(\omega)
		\end{split}
	\end{equation}

@@

	Then an OLS estimator can be calculated in the usual way to obtain an estimate for the values of $\alpha$ and $b_j$, and an estimate of the coefficient function can be derived accordingly.
	\begin{equation}
		b^L = \left(Z'Z\right)^{-1}Z'Y \in \mathbb{R}^{L+1} \quad \hat{\alpha} = b_{1}^{L} \quad \hat{\beta}^L(t) = \sum_{j = 1}^{J} b_{j+1}^L \phi_j(t)
	\end{equation}

@@

	\subsection{Motivation}\label{sim_motivation}
